Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-19 writeup/gz_hubble_data.tex
Reference Tom's findings of flat f_bar[z]

The resulting bar sample can be used to estimate the redshift evolution of bar
fraction and find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to
\fbar$\sim 0.24$ at $z=1.0$. The decrease in bar fraction agrees with
\citet{mel14}, although they report a lower overall bar fraction going from
\fbar$=0.22$ at $z=0.4$ to \fbar$=0.11$ at $z=1.0$. The difference in total bar
fraction is expected, as this analysis used a looser cut on \fbar, there is no
luminosity cut, and the use of debiased values for \ffeatures{} increases the
total amount of disks in the sample compared to \citet{mel14}. For a more
thorough analysis of the bar fraction, a cut on \fbar{} that evolves with
redshift may yield more accurate results, since there are no explicit debiased
values of \fbar{} that would take redshift induced bias into account.

>>>>

The resulting bar sample can be used to estimate the redshift evolution of bar
fraction and find a steady decrease of \fbar$\sim 0.32$ at $z=0.4$ to
\fbar$\sim 0.24$ at $z=1.0$. The decrease in bar fraction agrees with
\citet{mel14}, although they report a lower overall bar fraction going from
\fbar$=0.22$ at $z=0.4$ to \fbar$=0.11$ at $z=1.0$. The difference in total bar
fraction is expected, as this analysis used a looser cut on \fbar, there is no
luminosity cut, and the use of debiased values for \ffeatures{} increases the
total amount of disks in the sample compared to \citet{mel14}. However, the
results from GZH indicate that if features are reliably identified, the bar is
always visible; for galaxies at increasing redshifts, the discs fade first but
the galactic bar remains visible \citep{mel16}. As a result, we do \emph{not}
recommend using an evolving cut on \fbar{} as a function of redshift for the
selection of barred discs.
